\section{Decentralized Algorithm with Partial Information}
In this section, we first propose a low-complexity solution to the global optimization problem.
We introduce a heuristic dispatching algorithm as the baseline policy, whose value function could be derived analytically.
Then the right-hand-side of Bellman's Equation is replaced with the above approximated Bellman's equation, and the sub-optimal solution can be obtained with one-step policy iteration.
Hence, the derived approximated value function of the baseline policy becomes the cost upper bound of the proposed sub-optimal policy.

Moreover, we remove the assumption on centralized agent in the problem formulation, and APs iteratively apply policy update.
Under this scheme, we could further reduce the state information required for one AP and alleviate the impact of \brlatency.
Then we leverage the sub-optimal solution obtained above, and replace the expression with reduced state information.
% The whole solution procedure is as illustrated in Fig.\ref{fig:solution}.

\subsection{Low-Complexity Solution}
The baseline dispatching policy is adopted to obtain an approximation of value function. The policy on each AP nodes is state-invariant, which is denoted as:
\begin{align}
    \BaseLine(t) \define \Bracket{\Pi_1(t), \Pi_2(t), \dots, \Pi_K(t)},
\end{align}
where $\Pi_k(t) \define \set{\pi^{(k)}_{m,j}(t) | \forall m\in\esSet,\forall j\in\jSpace}$ denotes ($\forall k\in\apSet$) the action set resembling the definition in Eqn. (\ref{def_action}).
More specifically, $\BaseLine(t)$ is assumed as the stationary baseline policy adopted globally after the $t$-th broadcast and the baseline policies are different in each broadcast interval.

According to the additive structure of cost function, we substitute the transition function plus value function in Eqn. (\ref{eqn:sp_0}) with two linearly sections as $W^{\AP}(\mathcal{R}(t+1))$ and $W^{\ES}(\mathcal{Q}(t+1))$ under baseline policy $\BaseLine(t)$:
\begin{align}
    &V(\Stat(t)) = g(\Stat(t)) +
    \nonumber\\
    &~~~~~~\gamma \min_{\BaseLine(t)} \Bracket{ W^{\AP}_{\BaseLine(t)}\Paren{\mathcal{R}(t+1)} + W^{\ES}_{\BaseLine({i})}\Paren{\mathcal{Q}(t+1)} },
\end{align}
where $W^{\AP}_{\BaseLine(t)}(\cdot)$ and $W^{\ES}_{\BaseLine(t)}(\cdot)$ denote the split \emph{expected value function} over AP nodes and ES nodes, respectively, $\Policy(\Stat(t)) = \tilde{\Omega}({t-1}), \BaseLine(t)$. The split expected value functions are defined as follows.
\begin{align}
    W^{\AP}_{\BaseLine(t)}\Paren{\mathcal{R}(t)}
        &\define \sum_{k\in\apSet}\sum_{m\in\esSet}\sum_{j\in\jSpace}
        % \nonumber\\
        \mathbb{E}_{\{\BaseLine(t), \vec{R}^{(k)}_{m,j}(t)\}}\Bracket{
            \sum_{i=0}^{\infty} \gamma^{i} \Inorm{\vec{R}^{(k)}_{m,j}({t+i})}
        }
    \\
    W^{\ES}_{\BaseLine(t)}\Paren{\mathcal{Q}(t)}
        &\define \sum_{m\in\esSet}\sum_{j\in\jSpace}
        % \nonumber\\
        \mathbb{E}_{\{\BaseLine(t), Q_{m,j}(t)\}}\Bracket{
            \sum_{i=0}^{\infty} \gamma^{i} l_{m,j}({t+i})
        }.
\end{align}
        
The decoupled value functions for AP and ES nodes is obtained with an approximated form under the baseline policy. We use the same baseline policy to evaluate both low-complexity policy performance in Eqn. (\ref{eqn:sp_0}).

The expected value function $W^{\AP}(\mathcal{R}(t+1))$ under baseline $\vecG{\Pi}(t)$ for AP nodes is easily obtained by calculating by the following equation:
\begin{align}
    &W^{\AP}_{\BaseLine(t)}\Paren{\mathcal{R}(t+1)} = \sum_{k\in\apSet}\sum_{m\in\esSet}\sum_{j\in\jSpace}
    % \nonumber\\
    \Inorm{
        \Paren{1 - \gamma \hat{\Gamma}^{(k)}_{m,j}}^{-1}
        \times \vecG{\Theta}^{(k)}_{m,j}(t+1)
    },
    \label{w_ap}
\end{align}
where $\hat{\Gamma}^{(k)}_{m,j} \define (\Gamma^{(k)}_{m,j})^{N}$, $\Inorm{\cdot}$ denotes the sum of absolute value of each entry of the vector.
\delete{v4}{And the transition function $\Pr\{ \mathcal{R}(t+1)|\mathcal{R}(t) \}$ is embedded with its distributions $\vecG{\Theta}^{(k)}_{m,j}(t+1)$ in the equation.}

The expected value function $W^{\ES}(\mathcal{Q}(t+1))$ under baseline $\vecG{\Pi}(t)$ for ES nodes is little more complex compared to Eqn. (\ref{w_ap}).
The ES node transition is affected with both arrival process under dispatching policy and last queue state.
However, we notice that the arrival process would be stationary after the maximum uploading time under the stationary baseline policy and the relationship between APs and edge server could be decoupled.
\begin{align}
    &W^{\ES}_{\BaseLine(t)}\Paren{\mathcal{Q}(t+1)}
    \nonumber\\
    =& \sum_{m,j}\sum_{i=0,\dots,\frac{\Xi}{T}} \gamma^{i} \mathbb{E}[ Q_{m,j}({t+i+1}) ]
    \nonumber\\
    &~~~~~~~~+ \gamma^{\frac{\Xi}{T}} \Paren{ \mat{I} - \gamma \hat{\mat{P}}_{m,j}(\tilde{\beta}_{m,j}) }^{-1} \vecG{\nu}({t+\frac{\Xi}{T}+1}) \vec{g}',
\end{align}
where $\hat{\mat{P}}_{m,j}(\tilde{\beta}_{m,j}) \define \prod_{n=0,\dots,N-1} \mat{P}_{m,j}(\tilde{\beta}_{m,j})$;
the probability distribution of $Q_{m,j}({t+i+1})$ is denoted by $\vecG{\nu}({t+i+1})$ which is obtained by calculation over equation Enq. (\ref{eqn_0}) - Eqn. (\ref{eqn_4}) ($\forall i=0,\dots,\frac{\Xi}{T}$);
the $i$-th element of vector $\vec{g}$ denotes the cost of server as $l_{m,j}(t)$;
$\tilde{\beta}_{m,j}$ is the arrival distribution under baseline policy $\Pi(t)$ (on $m$-th ES with $j$-type job), where:
\begin{align}
    \tilde{\beta}_{m,j} &\define \sum_{k\in\apSet} \tilde{\lambda}^{(k)}_{m,j} \times \sum_{\xi=0,\dots,\Xi-1} \Pr\{ \xi<U_{k,m}\leq(\xi+1) \}
        \nonumber\\
    ~~~~&= \sum_{k\in\apSet} \tilde{\lambda}^{(k)}_{m,j}
\end{align}
%----------------------------------------------------------------------------------------%

\subsection{Problem Decoupling with Partial Observed Information}
\fixit{
    The AP would update its policy once receive the \emph{Observed State Information} (OSI).
    And we redefine the following concepts (for the $k$-th AP):
        1) \brlatency~due to OSI;
        2) policy mapping over OSI;
        3) baseline policy (t);
        4) the approximated expected value function;
    
    We restrict out observation in solution part, and just leverage the structure of the above centralized optimization problem.
    \begin{remark}
        Assume that we solve the sub-problems following the order of index of AP set, and then substitute the solution to the $k$-th problem to the $(k+1)$-th problem ($\forall k\in\apSet$).
        Apparently, we could achieve a sub-optimal solution of all APs which is upper bounded by the solution to the original problem.
    \end{remark}
}

% It's still impossible to evaluate the above Bellman's equation due to the complexity would increase exponentially with respect to number of APs and edge servers.
%NOTE: Conflict of AP set and partial information definition
In \comments{an extensive edge computing network residing in MAN}, it may not be feasible for each AP to collect the LSI from all other APs and edge servers.
Hence, we first define the \emph{conflict AP set} as follows.
\begin{align}
    \ccSet_{k} \define \bigcup_{m\in\esSet_{k}} \apSet_{m}
    % \ccSet_{k} \define \set{\forall k' \neq k\in\apSet|\esSet_{k'} \cap \esSet_{k} \neq \emptyset}
\end{align}
The \emph{conflict AP set} indicates that the subset of APs whose LSI could affect the decision making for the $k$-th AP.
It is assumed that each AP can only collect the LSI from the APs in its \emph{conflict AP set} and edge servers from its \emph{candidate server set}.
Hence, we refer to the reduced state information required as \emph{observed state information} (OSI) and the definition of the $k$-th AP is given as follows ($\forall k\in\apSet$).
\begin{definition}[Observed State Information]
    \begin{align}
        \Obsv_{k} &= \set{\mathcal{R}_{k'} | \forall k'\in\ccSet_{k}}
                        \cup \set{\mathcal{Q}_{m} | \forall m\in\esSet_{k}},
    \end{align}
\end{definition}

One AP will update its dispatching decision after the reception of its OSI, while the others will keep their previous policies.
We denote the individual dispatching policy of the $k$-th AP ($\forall k\in\apSet$) based on its OSI $\Obsv_{k}({t})$ as follows.
\begin{align}
    &\Omega_{k}(\Obsv_{k}(t)) \define \set{\omega'_{k,j}(t)|\forall m\in\esSet, j\in\jSpace}.
    \label{def_action}
\end{align}


\fixit{
    Hence, we only update the individual policy of the $k$-th AP ($\forall k\in\apSet$) at one time, and the Bellman's equation would reduce into the form as follows, where only the OSI (partial information) for the $k$-th AP matters.
    \begin{align}
        V_{k}\Paren{\Obsv_{k}({t})} =& g_{k}(\Obsv_{k}(t)) +
        \gamma\min_{\Omega_{k}(\Obsv_{k}(t))}
        \nonumber\\
        &\sum_{\Obsv_{k}(t+1)} \Pr
        \Brace{ 
            \Obsv_{k}(t+1) | \Obsv_{k}(t), \Omega_{k}(\Obsv_{k}(t))
        } \cdot V_{k}\Paren{\Obsv_{k}({t+1})},
    \end{align}
    where,
    \begin{align}
        g_{k}(\Obsv_{k}(t)) \define& \sum_{j\in\jSpace} \Brace{
            \sum_{k\in\mathcal{X}_{k}} \sum_{m\in\esSet_{k}} \vec{R}^{(k)}_{m,j}(t) +
            \sum_{m\in\esSet_{k}} \set{ L_{m,j}(t) + \beta \cdot \mat{I}[L_{m,j}(t)=L_{max}] }
        }
    \end{align}
}
%----------------------------------------------------------------------------------------%

\subsection{The Decentralized Algorithm}
\fixit{
    \begin{itemize}
        \item We leverage the global optimization problem, while the presence of $\mathcal{D}(t)$ doesn't matter in our algorithm;
        \item We propose one iterative update algorithm (elaboration needed);
        \item The performance bound is guaranteed, and always better compared with last stage.
    \end{itemize}
}

The optimization problem at right-hand side of approximate Bellman's Equation is given as follows.
\begin{align}
    \min_{\BaseLine(t)} W^{\AP}_{\BaseLine(t)}\Paren{\mathcal{R}(t+1)} + W^{\ES}_{\BaseLine(t)}\Paren{\mathcal{Q}(t+1)}
    \label{eqn_opt}
\end{align}

Then we introduce the iterative policy update algorithm, which optimize the 
with improved baseline policy in each interval as performance guarantee.
\begin{itemize}
    \item Choose initial policy $\Policy(\Stat(0)) = \BaseLine(0)$ as start, which is the \emph{local greedy policy};
    \item In $t\in[0, 1)$, the AP node indexed with $1$ would receive the broadcast information after $D_1(1)$ and updates the global information; then it solves the optimization problem in Eqn. (\ref{eqn_opt}) with only $\Pi_{1}(1)$ changes in $\Policy(\Stat(1)) = \BaseLine(1) = [\Pi_{1}(1), \Pi_{2}(0), \dots, \Pi_{K}(0)]$;
    \item At $t=1$, the AP node indexed with $1$ would broadcast its policy $\Pi_{1}(1)$ together with the state information;
    \item In $t\in[1, 2)$, the AP nodes indexed with $2$ would receive the broadcast information and previous global policy $\Policy(\Stat(1))$; then it repeats the procedure what the $1$-st AP did;
    \item Then generally, in $t\in[{i}, {i+1})$, the AP nodes indexed with $(k \mod K)+1$ would update its own policy following the above procedure.
\end{itemize}

\begin{lemma}
    The optimized policy solved as $\BaseLine(t)$ (for next stage), is better than $\BaseLine(t-1), \dots, \BaseLine(1)$ when considering the \emph{approximated value function} defined above.
    \\
    Moreover, the performance of the series of the baseline policies is upper bounded by the optimal solution $\Policy^*$ when considering the original Bellman's equation.
\end{lemma}
\begin{proof}
    \fixit{
        The proof is illustrated into two parts.
        \begin{itemize}
            \item $\BaseLine(t)$ is better than the previous baseline policy, \emph{with the latest start} $\Obsv(t+1)$; the other previous policies were determined from the different start state;
            \item Upper bound is easy to prove with one-step iteration that:
            $$
                V_{\Omega^*}\Paren{\Stat(t)}
                    \leq W_{\BaseLine(t)}\Paren{\Stat(t)}
                    \leq W_{\BaseLine(t-1)}\Paren{\Stat(t)}
                    \leq \dots \leq W_{\Pi(1)}\Paren{\Stat(t)}
            $$
            but I doube this could not stand, cause the stationary policy is also affected by \emph{start state} and \emph{random broadcat delay}.
        \end{itemize}
    }
\end{proof}

%----------------------------------------------------------------------------------------%
\delete{v7}{
    To better analyze the structure of the optimization problem, we decouple the transition function.
    The decoupled transition function for Eqn. (\ref{eqn:sp_0}) is given as follows.
    The expression of transition function in Eqn. (\ref{eqn:sp_0}) is given as follows.
    The transition function is consisted of two parts of state transitions on APs and edge servers, respectively.
    To efficiently express the state transition, we further elaborate the distribution probability of the state vector as the corresponding probability vector, and perform the state transition with the transition matrix.

    %NOTE: transition matrix and vector for AP
    For state transition of APs inside one interval, we denote $\vecG{\Theta}^{(k)}_{m,j}(t,n)$ and ${\Gamma}^{(k)}_{m,j}(t,n)$ as probability vector and transition matrix, respectively, for $\vec{R}^{(k)}_{m,j}(t,n)$ of the $j$-th type of job uploading from the $k$-th AP to the $m$-th edge server ($\forall k\in\apSet, m\in\esSet, j\in\jSpace$). The definition is given as follows.
    \begin{align}
        \Gamma^{(k)}_{m,j}(t,n) \define
        \begin{bmatrix}
            1 & \bar{p}^{(k)}_{m,j,0} &                       &        &                           \\
            & 0                     & \bar{p}^{(k)}_{m,j,1} &        &                           \\
            &                       & \ddots                & \ddots &                           \\
            &                       &                       & \ddots & \bar{p}^{(k)}_{m,j,\Xi-1} \\
            &                       &                       &        & 0                         \\
        \end{bmatrix},
        \vecG{\Theta}^{(k)}_{m,j}(t,n) \define
        \begin{bmatrix}
            \theta^{(k)}_{m,j,0}(t,n) \\
            \theta^{(k)}_{m,j,1}(t,n) \\
            \vdots \\
            \vdots \\
            \theta^{(k)}_{m,j,\Xi}(t,n)
        \end{bmatrix},
    \end{align}
    where $p^{(k)}_{m,j,\xi} \define \Pr\{U^{(k)}_{m,j} < (\xi+1) | U^{(k)}_{m,j}>\xi\}$ and $\bar{p}^{(k)}_{m,j,\xi} = 1 - p^{(k)}_{m,j,\xi}$ denote the probability of staying and offloading, respectively; $\theta^{(k)}_{m,j,\xi}(t,n) \define \Pr\{R^{(k)}_{m,j,\xi}(t,n) = 1\}$ denotes the distribution probability of existing job in the corresponding counters of the AP ($\forall \xi=0,\dots,\Xi$).

    And we note that $\theta^{(k)}_{m,j,0}(t,n)$ is purely determined by the arrival process and dispatching policy of the $j$-th type of job on the $k$-th AP, i.e. $\theta^{(k)}_{m,j,0}(t,n) = \lambda_{k,j} I[\omega_{k,j}(t,n) = m]$, where $I[\cdot]$ is the indicator function.
    Hence, the state transition between adjacent interval from $\vecG{\Theta}^{(k)}_{m,j}(t+1)$ to $\vecG{\Theta}^{(k)}_{m,j}(t)$ is composed of two-phase policy separated by $D_k(t)$, which could be expressed as follows.
    \begin{align}
        \vecG{\Theta}^{(k)}_{m,j}(t, D_{k}(t)) &= (\Gamma^{(k)}_{m,j})^{D_{k}(t)} \times \vecG{\Theta}^{(k)}_{m,j}(t),
        \nonumber\\
        \vecG{\Theta}^{(k)}_{m,j}({t+1}) &= (\Gamma^{(k)}_{m,j})^{N-D_{k}(t)} \times \vecG{\Theta}^{(k)}_{m,j}(t, D_{k}(t)).
    \end{align}

    %NOTE: small probability approximation
    For state transition of edge servers, we denote $\vecG{\mu}_{m,j}$ and $P_{m,j}$ as probability vector and transition matrix, respectively, for $Q_{m,j}$ of the $j$-th job processing on the $m$-th edge server ($\forall m\in\esSet, j\in\jSpace$). The definition of the probability vector $\vecG{\mu}_{m,j}(t,n)$ at the $n$-th time slot in the $t$-the interval is given as follows.
    \begin{align}
        \vecG{\mu}_{m,j}(t,n) \define 
        \begin{bmatrix}
            &\Pr\{L_{m,j}(t,n)=0,   &        & \eta_{m,j}(t,n)=0\} \\
            &\Pr\{L_{m,j}(t,n)=0,   &        & \eta_{m,j}(t,n)=1\} \\
            &                       & \vdots & \\
            &\Pr\{L_{m,j}(t,n)=0,   &        & \eta_{m,j}(t,n)=\mathcal{C}_{m,j}-1\} \\
            &\Pr\{L_{m,j}(t,n)=1,   &        & \eta_{m,j}(t,n)=0\} \\
            &                       & \vdots & \\
            &\Pr\{L_{m,j}(t,n)=L_{max}, &        & \eta_{m,j}(t,n)=\mathcal{C}_{m,j}-1\}
        \end{bmatrix}
    \end{align}
    However, the expression of transition matrix $P_{m,j}$ is more complex. Firstly, we notice that in the transition function of edge server, the distribution of offloading number of jobs from all APs in the interval contributes to the job arrival process on edge server as $\mathcal{R}(t)$. We denote the offloading matrix $\bar{\Gamma}^{(k)}_{m,j}$ from each AP to the $m$-th edge server as follows.
    \begin{align}
        \bar{\Gamma}^{(k)}_{m,j}(t,n) \define
        \begin{bmatrix}
            0 & p^{(k)}_{m,j,0} &                 &        &                     \\
            & 0               & p^{(k)}_{m,j,1} &        &                     \\
            &                 & \ddots          & \ddots &                     \\
            &                 &                 & \ddots & p^{(k)}_{m,j,\Xi-1} \\
            &                 &                 &        & 1                   \\
        \end{bmatrix},
    \end{align}
    And the offloading number vectors are denoted as follows.
    \begin{align}
        \vecG{\rho}^{(k,+)}_{m,j}({t,n}) &\define \bar{\Gamma}^{(k)}_{m,j} \times \vecG{\theta}^{(k)}_{m,j}({t,n}),
    \end{align}
    and the arrival number at the $n$-th time slot in the $t$-th interval on the $m$-th server is $\sum_{k\in\apSet} \vecG{\rho}^{(k,+)}_{m,j}({t,n})$,
    The dimension of the compounded vector would be un-acceptable, as the increase of AP numbers would result into exponential expansion of dimensionality.
    Thus we rewrite the arrival process on edge server with small probability approximation, i.e. there would be at most one job arring in one time slot, with the probability as the expected arrival rate of the original distribution. The explicit definition of the approximate arriving probability $\beta_{m,j}({t,n})$ is given as follows.
    \begin{align}
        {\beta}_{m,j}({t,n}) &\define \sum_{k\in\mathcal{K}} \sum_{\xi=0,\dots,\Xi-1} \mathbb{E}[\vecG{\rho}^{(k,+)}_{m,j,\xi}({t,n})]
        \label{eqn_0}
    \end{align}
    We could prove that the error due to approximation is negligible.
    \begin{lemma}[Small Probability Approximation]
        The probability distribution of $\sum_{k\in\apSet} \vecG{\rho}^{(k,+)}_{m,j}({t,n})$ could be approximated with Bernoulli arrival process with the same expected arrival rate denoted as ${\beta}_{m,j}({t,n})$.
    \end{lemma}
    \begin{proof}
        \fixit{
            We notice that the job arrival distribution ${\beta}_{m,j}(t)$ is given by $\mathcal{R}(t)$, and the departure rate in one slot is deterministic as $1/N$.
            Thus the expectation of ${\beta}$ would be always far more smaller than $1$ as composed of all $K$ AP nodes.
            We take approximation on ${\beta}$ as Bernoulli distribution in each time slot.
        }
    \end{proof}

    %NOTE: transition matrix and vector for ES
    Thus we could obtain the time-variant transition matrix composed of multiple transition matrix $P_{m,j}(\beta({t,n}))$ in all the time slots in $i$-th interval as follows.
    \begin{align}
        \vecG{\nu}({t,n+1}) &= P_{m,j}\Paren{\beta_{m,j}({t,n})} \vecG{\nu}({t,n})
        % \label{eqn_3}
        \\
        \vecG{\nu}({t+1}) &= \prod_{n=0,\dots,N-1} P_{m,j}\Paren{\beta_{m,j}({t,n})} \vecG{\nu}(t),
        \label{eqn_4}
    \end{align}

    % [\IF, \ENDIF], [\FOR, \TO, \ENDFOR], [\WHILE, \ENDWHILE], \STATE, \AND, \TRUE
    % \begin{algorithm}[H]
    %     \caption{Online Iterative Policy Improvement Algorithm}
    %     \begin{algorithmic}[1]
    %         \STATE $t = 0$
    %         \FOR{$t = 1,2,\dots$}
    %             \STATE Evaluate $\Omega_0$ in \textbf{P1} according to Eqn. \ref{sp1}
    %             \FOR{$k \in \mathcal{K}$}
    %                 \STATE fix policy $\vec{\Omega}^{(k)}(t) \forall k' < k$
    %                 \STATE Evaluate $k$-th AP Local Policy $\tilde{\Omega}_k$ in \textbf{Pk} according to Eqn. \ref{sp2}
    %             \ENDFOR
    %         \ENDFOR
    %     \end{algorithmic}
    % \end{algorithm}
}
%----------------------------------------------------------------------------------------%